Quality Definitions of Qualities

### 2021-10-11 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added reasoning for unambiguity definition

\begin{defn}
 A Software Requirements Specification (SRS) is unambiguous if, and only if,
 every requirement stated therein has only one interpretation \citep{IEEE1998}.
\end{defn}

@@

\begin{mybox}
\subsubsection*{Unambiguity} 
Definition~\ref{UnambiguitySelected} rephrased: Unambiguity is the quality of having one clear interpretation, and not having any other possible interpretations.
\end{mybox}

@@

\begin{itemize}
  \item This definition succinctly encompasses parts of the chosen definition, and includes the basis of the alternate definition.
\end{itemize}

>>>>

\begin{defn}
 \label{IEEEunambiguity}A Software Requirements Specification (SRS) is unambiguous if, and only if,
 every requirement stated therein has only one interpretation \citep{IEEE1998}.
\end{defn}

@@

\begin{mybox}
\subsubsection*{Unambiguity} 
Unambiguity is the quality of having one clear interpretation, and not having any other possible interpretations.
\end{mybox}

@@

The recommended definition comes from rephrasing Definition \ref{UnambiguitySelected} while keeping in mind its similarities with Definition \ref{IEEEunambiguity}. The rationale for the proposed definition follows:

\begin{itemize}
  \item Definition \ref{IEEEunambiguity} mentions the ``Software Requirements Specification'' document and, the specifically related term, ``requirement''. We feel that for the sake of abstraction we should not have the definition focus solely on this specific document and its related term, so we do not include these in the chosen definition.
  \item The term ``interpretation'' is found in both Definition \ref{IEEEunambiguity} and Definition \ref{UnambiguitySelected} and is kept in the chosen definition.
  \item The first two part of Definition \ref{UnambiguitySelected} can be succinctly restated as ``having one interpretation''.
  \item The fourth part of Definition \ref{UnambiguitySelected} can be added to the above phrase, resulting in the new phrase ``having one clear interpretation''. This removes the possibility of one vague interpretation, also addressing the third part of Definition \ref{UnambiguitySelected}.
  \item The new phrase ``having one clear interpretation'' is still ambiguous as there could be one clear interpretation, and one or more vague interpretations. This is addressed by adding a phrase stating that there are no other possible interpretations besides the one clear interpretation.
\end{itemize}
